Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-13 mpaper/paper.tex
Committing before an attempt at fixing problematic numerical errors

\section{Evaluation} % showing deep understanding
% Could measure how algorithms scale with the size of the map (number of states)
% Mention all the constants I've used.
% How well does the variance prediction work?

%\begin{figure} % this is more confusing than helpful
%  \centering
%  \begin{tikzpicture}
%    \node [ellipse,draw] (s1) at (-1, -1) {$s_1$};
%    \node [ellipse,draw] (s2) at (0, 0) {$s_2$};
%    \node [ellipse,draw] (s3) at (1, -1) {$s_3$};
%    \draw [->,-to,bend left] (s1) edge (s2);
%    \draw [->,-latex,dashed] (s1) edge (s3);
%    \draw [->,-to] (s2) edge (s1);
%    \draw [->,-latex,bend left,dashed] (s2) edge (s3);
%    \draw [->,-to,bend left,dashed] (s3) edge (s1);
%    \draw [->,-latex] (s3) edge (s2);
%  \end{tikzpicture}
%\end{figure}

%\printinunitsof{cm}\prntlen{\textwidth}
%\printinunitsof{cm}\prntlen{\textheight}
%\printinunitsof{cm}\prntlen{\columnwidth}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{elbo_contour_plots}
\end{figure*}

@@

@@

%Our work also poses a new challenge to the usual methods of determining an
%optimal strategy in a given MDP:
%\begin{problem}
%  Let $\mathcal{M} = \{ \mathcal{S}, \mathcal{A}, \mathcal{T}, \gamma,
%  r \}$ be an MDP where the reward $r : \mathcal{S} \to
%  \textsf{Prob}(\mathbb{R})$ is expressed as a function from the set of states
%  to the set of probability distributions with support over $\mathbb{R}$. Find
%  the optimal policy $\pi^*$ in $\mathcal{M}$, i.e., % TODO: argmax expression
%\end{problem}
%Of course, in many situations,... % TOOD: gaussians, pdf's, something simpler

\begin{itemize}
\item MDP solver that works with distributions of rewards.
\item Stress how solving MDPs is the performance bottleneck: numSamples MDPs
  have to be solved for each iteration.
  \begin{itemize}
  \item Integration with MDP solvers that approximate the value function
    sufficiently well for training.
  \item Or perhaps there is a way to ``modify'' a solution to one MDP in order
    to get a solution for a similar MDP (there was a FATA talk about that, but
    for a different problem of course).
  \item Perhaps value iteration converges faster if the values are initialised
    to the optimal values of the previous iteration.
  \end{itemize}
\end{itemize}

>>>>

\section{Evaluation} % showing deep understanding
% Mention all the constants I've used.

@@

 % TODO: need to redo this to get better labels, more precision, wider range of values
\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{elbo_contour_plots}
\end{figure*}

@@

% How does policy depend on rewards? Choose state and action, generate an array
% of contour plots showing the probability of taking that action in an optimal policy
Observation from a plot not worth including here. The policy behaves as
expected: if we fix $r(s_1)$, $\pi(s_1, a_1)$ increases with higher $r(s_2)$ as
well as lower $r(s_3)$ values.

% How well does the variance prediction work?

@@

It is also worth noting the approach presented in this paper requires solving
$S$ MDPs for every iteration of optimising the parameters (where $S$ is the
number of samples drawn from $\approximation$). There are at least two ways to
reduce or eliminate this performance bottleneck:
\begin{itemize}
\item The MDP value function could be approximated, allowing for some minor
  mistakes in the resulting policy.
\item Perhaps there is a good way to use information about previously computed
  value functions for similar rewards to hasten the current computation. One
  simple way to do this would be by initialising the current values to the
  optimal values of the previous MDP value function computation.
\end{itemize}
